Msprime 1.0: an efficient and extensible coalescent simulation framework

### 2021-07-18 paper.tex
Comment out out-of-date roadmap text.

\jkcomment{We should trim this down quite a bit - all we want to do is some basic
roadmapping, like, we discuss the underlying tree sequence object,
then mutations (because it's quite separate from the rest)
and then a bunch of new features for ancestry simulation. There's no
point in listing it out section by section.}
In this section we describe the main features of \msprime\ 1.0. Methodologically,
there exists a logical separation between simulating coalescent genealogies and
adding neutral mutations onto these genealogies. Simulating genetic ancestry
requires methods that model the underlying reproductive process (e.g. Moran,
Wright-Fisher, etc.) as well as accounting for recombination of various sorts
(including gene conversion), demography, and selection. These methods are
discussed in the first N subsections below. One of the strengths of the
approach taken in msprime is that neutral mutations can be retrospectively
added to simulated genealogies. Methods to generate mutations, and thereby
generate genetic variation, are therefore discussed in a separate and subsequent
subsection. Finally, we describe the \msprime\ API, which is designed to enforce
the distinction between simulating genealogies and mutations; discuss the
interoperability provided by the use of \tskit\, the tree sequence toolkit;
and highlight the open source development process which allows for \msprime\
to be extended by addition of new features while ensuring robustness and
maintainability of the core codebase.

>>>>

\jkcomment{Give a quick roadmap,
like, we discuss the underlying tree sequence object,
then mutations (because it's quite separate from the rest)
and then a bunch of new features for ancestry simulation. There's no
point in listing it out section by section.}

% JK: commented out this text as it's misleading and would confuse
% people. We should adapt it when writing the roadmap when the structure
% has settled down.

% In this section we describe the main features of \msprime\ 1.0. Methodologically,
% there exists a logical separation between simulating coalescent genealogies and
% adding neutral mutations onto these genealogies. Simulating genetic ancestry
% requires methods that model the underlying reproductive process (e.g. Moran,
% Wright-Fisher, etc.) as well as accounting for recombination of various sorts
% (including gene conversion), demography, and selection. These methods are
% discussed in the first N subsections below. One of the strengths of the
% approach taken in msprime is that neutral mutations can be retrospectively
% added to simulated genealogies. Methods to generate mutations, and thereby
% generate genetic variation, are therefore discussed in a separate and subsequent
% subsection. Finally, we describe the \msprime\ API, which is designed to enforce
% the distinction between simulating genealogies and mutations; discuss the
% interoperability provided by the use of \tskit\, the tree sequence toolkit;
% and highlight the open source development process which allows for \msprime\
% to be extended by addition of new features while ensuring robustness and
% maintainability of the core codebase.
